### 2021-04-18 README.Rmd
Add Travis CI to the package
Slight updates to the README, added parameters to the summary plot function to make it more robust
Added tests for all functions, fixed some small bugs in the mSHAP function.

<!-- badges: start -->
<!-- badges: end -->

@@

```{r}
## R
cost_per_month <- (0.0006 * income - 0.2 * sex + 0.5 * married - 0.001 * age) + 10
num_months <- (0.0001 * income + 0.0001 * sex + 0.05 * married - 0.05 * age) + 3
```

@@

```{r, fig.width=5, fig.height=5,fig.align='center'}
## R
observation_plot(
  variable_values = X[46,],
  shap_values = final_shap$shap_vals[46,],
  expected_value = final_shap$expected_value,
  names = c("age", "income", "married", "sex")
)
```

>>>>

<!-- badges: start -->
<!--[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)-->
<!-- badges: end -->

@@

```{r}
## R
cost_per_month <- (0.0006 * income - 0.2 * sex + 0.5 * married - 0.001 * age) + 10
num_months <- 15 * (0.001 * income  * 0.001 * sex * 0.5 * married - 0.05 * age)^2
```

@@

```{r, fig.width=5, fig.height=5,fig.align='center'}
## R
observation_plot(
  variable_values = X[23,],
  shap_values = final_shap$shap_vals[23,],
  expected_value = final_shap$expected_value,
  names = c("age", "income", "married", "sex")
)
```

For another, more complex, use case run `vignette("mshap")`.
For more examples and options for plotting, run `vignette("mshap_plots")`.
